Multi-task learning in Computer Vision

### 2020-05-31 4-Object-detection.tex
Add final chapter recap and other minor fixes

\section{Metrics}
The training of object detection models requires data sets that have been labeled for that purpose.
Generally, the data sets contain bounding box annotations for each of the classes in the data set, such as seen in Figure 5.1.
For this reason, object detection models can't use a simple metric like the basic accuracy in image classification.
As the images are often manually labeled, the boxes are most likely not completely consistent.
So most likely, the predictions are never going to align with the labeled boxes perfectly.
Consequently, the method for evaluating object detection performance is Average Precision (AP) or mean Average Precision (mAP) or one of their variants.
These metrics use intersection over union (IoU) score to evaluate how incorrect the predicted bounding box is when compared to the actual label. Intersection over union is visualized in Figure 5.1.

@@

The head is where the architectures differ the most, and generally, any backbone could be combined with a specific detector head.
The head comprises of a neck, which connects the intermediate features from the backbone to the final head.
The intermediate features are generally connections from some specific layers of the backbone.
Earlier single-stage detectors used the extracted features directly, but the current state-of-the-art methods use special feature pyramids and path aggregation to get the best results \citep{efficientDet}.
For example, the YOLO v4 uses spatial pyramid pooling \citep{SPP} over the DarkNet features and path aggregation net (PANet) \citep{PANET} to concatenate the parameters for the classifier head \citep{yolov4}.
Different ways of combining the feature pyramids are described in Figure 5.2.
Like many other parts of the architecture, picking one is a trade-off of more parameters and inference time and accuracy.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{imgs/detector_necks.png}
    \caption{a) Basic FPN \citep{FPN} where features are combined in only one direction. b) PANet modifies the basic FPN by adding a path from the lower level features to higher-level features. d) Fully-connected FPN requires a lot of extra features. f) BiFPN tries to prune the connections to the most important ones.}
\end{figure}

@@

\section{EfficientDet}
EfficientDet \citep{efficientDet} is an object detection model, that is based on the previously covered EfficientNet ImageNet model.
The neck for the EfficientDet is a unique bidirectional feature pyramid network (BiFPN).
The EfficientDet model also uses similar compound scaling as the EfficientNet models for the new object detection specific parts.
The scaling factor is used for the BiFPN network, box and class predictor networks, and to find the optimal input resolution.
The EfficinetDet shows that improving the backbone is quite useful for the entirety of the model.
This can especially be seen when looking at the comparisons of using a ResNet vs an EfficientNet as the backbone in the same EfficientDet architecture \citep{efficientDet}.
The EfficientDet model architecture is shown in Figure 5.3.

@@

The different feature maps in the BiFPN are combined using a weighted feature fusion.
The feature maps can't be directly combined since they have different dimensionality, so they have to be up or downsampled depending on the direction of the connection.
By weighing each feature map, the network can learn how important each feature map is.
Since the dimensionalities differ from one another, they likely don't contribute equally to the output feature maps, which is signified by the learned weight.
The BiFPN connection architecture is a simplified version of the PANet, as shown in Figure 5.2.
The goal of the changes from PANet is to have a more high-level fusion of features while dropping the nodes that have little feature fusion and then to stack multiple of these layers to get the final model \citep{efficientDet}.

@@

Once the exact architecture has been chosen, an implementation of it is needed to construct the model.
Generally, all the popular architectures have open-source implementations on GitHub in both Tensorflow and Pytorch, which are the most popular deep learning frameworks, that can be used.
Most of these implementations come quite readily wrapped in a way that given a correctly formatted data set, the models will be automatically initialized with the correct number of classes, and the training process is already specified by the input of a few necessary parameters.
As mentioned in the case of image classification, it is extremely important to initialize with the pre-trained weights with an object detection model to achieve the best results instead of training from scratch.
In an object detector, the problem-specific part is the number of classes in the classification head, which can be seen in Figure 5.3.
For the rest of the network, pre-trained weights should be used.

@@

Finally, once a model has been trained with a suitable dataset, architecture, and hyperparameters, it can output predictions for new images.
If the model is used without any modifications, the output boxes will likely look like the predictions in Figure 5.4.
To fix this issue in the predictions, non-max suppression (NMS) should be used \citep{nms}.
With non-max suppression, we can achieve only a single bounding box that better represents what is most likely wanted.
In some cases, using NMS can lead to not being able to predict heavily overlapping classes.
Generally, though NMS should pretty much always be used to avoid the issue depicted in the Figure 5.4.

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{imgs/obj-det.png}
    \caption{Object detection image labeled for people and cars.}
\end{figure}

\section{Metrics}
The training of object detection models requires data sets that have been labeled for that purpose.
Generally, the data sets contain bounding box annotations for each of the classes in the data set, such as seen in Figure 5.1.
For this reason, object detection models can't use a simple metric like the basic accuracy in image classification.
As the images are often manually labeled, the boxes are most likely not completely consistent.
So most likely, the predictions are never going to align with the labeled boxes perfectly.
Consequently, the method for evaluating object detection performance is Average Precision (AP) or mean Average Precision (mAP) or one of their variants.
These metrics use intersection over union (IoU) score to evaluate how incorrect the predicted bounding box is when compared to the actual label. Intersection over union is visualized in Figure 5.2.

@@

The head is where the architectures differ the most, and generally, any backbone could be combined with a specific detector head.
The head comprises of a neck, which connects the intermediate features from the backbone to the final head.
The intermediate features are generally connections from some specific layers of the backbone.
Earlier single-stage detectors used the extracted features directly, but the current state-of-the-art methods use special feature pyramids and path aggregation to get the best results \citep{efficientDet}.
For example, the YOLO v4 uses spatial pyramid pooling \citep{SPP} over the DarkNet features and path aggregation net (PANet) \citep{PANET} to concatenate the parameters for the classifier head \citep{yolov4}.
Different ways of combining the feature pyramids are described in Figure 5.3.
Like many other parts of the architecture, picking one is a trade-off of more parameters and inference time and accuracy.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{imgs/detector_necks.png}
    \caption{a) Basic FPN \citep{FPN} where features are combined in only one direction. b) PANet modifies the basic FPN by adding a path from the lower level features to higher-level features. d) Fully-connected FPN requires a lot of extra features. f) BiFPN tries to prune the connections to the most important ones.}
\end{figure}

@@

\section{EfficientDet}
EfficientDet \citep{efficientDet} is an object detection model, that is based on the previously covered EfficientNet ImageNet model.
The neck for the EfficientDet is a unique bidirectional feature pyramid network (BiFPN).
The EfficientDet model also uses similar compound scaling as the EfficientNet models for the new object detection specific parts.
The scaling factor is used for the BiFPN network, box and class predictor networks, and to find the optimal input resolution.
The EfficinetDet shows that improving the backbone is quite useful for the entirety of the model.
This can especially be seen when looking at the comparisons of using a ResNet vs an EfficientNet as the backbone in the same EfficientDet architecture \citep{efficientDet}.
The EfficientDet model architecture is shown in Figure 5.4.

@@

The different feature maps in the BiFPN are combined using a weighted feature fusion.
The feature maps can't be directly combined since they have different dimensionality, so they have to be up or downsampled depending on the direction of the connection.
By weighing each feature map, the network can learn how important each feature map is.
Since the dimensionalities differ from one another, they likely don't contribute equally to the output feature maps, which is signified by the learned weight.
The BiFPN connection architecture is a simplified version of the PANet, as shown in Figure 5.3.
The goal of the changes from PANet is to have a more high-level fusion of features while dropping the nodes that have little feature fusion and then to stack multiple of these layers to get the final model \citep{efficientDet}.

@@

Once the exact architecture has been chosen, an implementation of it is needed to construct the model.
Generally, all the popular architectures have open-source implementations on GitHub in both Tensorflow and Pytorch, which are the most popular deep learning frameworks, that can be used.
Most of these implementations come quite readily wrapped in a way that given a correctly formatted data set, the models will be automatically initialized with the correct number of classes, and the training process is already specified by the input of a few necessary parameters.
As mentioned in the case of image classification, it is extremely important to initialize with the pre-trained weights with an object detection model to achieve the best results instead of training from scratch.
In an object detector, the problem-specific part is the number of classes in the classification head, which can be seen in Figure 5.4.
For the rest of the network, pre-trained weights should be used.

@@

Finally, once a model has been trained with a suitable dataset, architecture, and hyperparameters, it can output predictions for new images.
If the model is used without any modifications, the output boxes will likely look like the predictions in Figure 5.5.
To fix this issue in the predictions, non-max suppression (NMS) should be used \citep{nms}.
With non-max suppression, we can achieve only a single bounding box that better represents what is most likely wanted.
In some cases, using NMS can lead to not being able to predict heavily overlapping classes.
Generally, though NMS should pretty much always be used to avoid the issue depicted in the Figure 5.5.

### 2020-05-31 5-Multitask.tex
Add final chapter recap and other minor fixes

\section{Hard parameter sharing}
A hard parameter sharing setting is one where the same convolutional weights in the intermediate layers solve multiple tasks, like in Figure 3.1.
Hard parameter sharing is the primary way of reducing total model size and inference time when solving multiple tasks simultaneously.
While sharing the weights can provide many benefits to the end model, as seen in the previous chapter, it comes at the cost of an increased number of tunable parameters when training the models. 
As we have previously seen, multi-task models introduce new constant factors to the training process beyond the normal hyperparameters for learning rate, dropout rate, and others.
These include the hyperparameters for weighing the loss functions and determining the task sampling ratios, but also the expensive to evaluate architectural decision of which tasks should share representations and how much should be shared.

@@

A similar multi-task model in \citep{visualPerson}, also partly visualized in Figure 3.1, solves 6 different tasks in a single model.
The tasks in that model are very different from one another, including person re-identification, pose estimation, and image segmentation.
The interesting result in their search for related tasks is that while a pair of tasks don't work well together, they can work well when combined with other tasks.
For example, they found that just pairing the pose estimation head with other tasks significantly reduces its accuracy, but when all tasks use the single shared backbone, it does just as well as if trained in a single-task setting.
These results show that very different tasks can combine to a single model to provide a very significant reduction in model size while producing about as good or better accuracies.

@@

The sharing functionality can be more complicated than just basic regularization. 
For example, the Cross-stitch units \citep{crossStitch} are a particular type of soft sharing, where the stitch units combine tasks A and B using a linear combination of the activations, visualized in Figure 3.2. 
The benefit here is that the user does not need to specify how much should be shared between the tasks, but it is instead learned in the cross-stitch unit. 
If nothing needs to be shared, then the network can learn to assign the weight for the other task to zero.

@@

An attempt to create a taxonomy of related tasks called Taskonomy to find out what tasks are beneficial for transfer learning exists in \citep{taskonomy}. 
The Taskonomy experiments pre-trained networks on tasks and then evaluated whether the features would transfer well to other tasks to end up with a hierarchical categorization of related tasks, shown in Figure 3.2. 
Still, the authors noted that, depending on model architecture and data set, the results could be different.

>>>>

\section{Hard parameter sharing}
A hard parameter sharing setting is one where the same convolutional weights in the intermediate layers solve multiple tasks, like in Figure 4.1.
Hard parameter sharing is the primary way of reducing total model size and inference time when solving multiple tasks simultaneously.
While sharing the weights can provide many benefits to the end model, as seen in the previous chapter, it comes at the cost of an increased number of tunable parameters when training the models. 
As we have previously seen, multi-task models introduce new constant factors to the training process beyond the normal hyperparameters for learning rate, dropout rate, and others.
These include the hyperparameters for weighing the loss functions and determining the task sampling ratios, but also the expensive to evaluate architectural decision of which tasks should share representations and how much should be shared.

@@

A similar multi-task model in \citep{visualPerson}, also partly visualized in Figure 4.1, solves 6 different tasks in a single model.
The tasks in that model are very different from one another, including person re-identification, pose estimation, and image segmentation.
The interesting result in their search for related tasks is that while a pair of tasks don't work well together, they can work well when combined with other tasks.
For example, they found that just pairing the pose estimation head with other tasks significantly reduces its accuracy, but when all tasks use the single shared backbone, it does just as well as if trained in a single-task setting.
These results show that very different tasks can combine to a single model to provide a very significant reduction in model size while producing about as good or better accuracies.

@@

The sharing functionality can be more complicated than just basic regularization. 
For example, the Cross-stitch units \citep{crossStitch} are a particular type of soft sharing, where the stitch units combine tasks A and B using a linear combination of the activations, visualized in Figure 4.3. 
The benefit here is that the user does not need to specify how much should be shared between the tasks, but it is instead learned in the cross-stitch unit. 
If nothing needs to be shared, then the network can learn to assign the weight for the other task to zero.

@@

An attempt to create a taxonomy of related tasks called Taskonomy to find out what tasks are beneficial for transfer learning exists in \citep{taskonomy}. 
The Taskonomy experiments pre-trained networks on tasks and then evaluated whether the features would transfer well to other tasks to end up with a hierarchical categorization of related tasks, shown in Figure 4.4. 
Still, the authors noted that, depending on model architecture and data set, the results could be different.

### 2020-05-31 7-Experiments.tex
Add final chapter recap and other minor fixes

\section{Basic multiple object classification tasks}
As we have previously covered, fine-tuning an ImageNet classifier often produces good results. 
Here we will take a pre-trained ImageNet backbone and learn multiple object classification tasks using the shared image embedding.
First, we will use two datasets that both contain images of healthy and unhealthy plants.

@@

\section{Object detection}
In this section, we will use multiple data sources and combine them into a single powerful object detector.
To be specific, our goal is to create an object detector for 37 different cat and dog species.
The two datasets that we will use are the COCO dataset \citep{COCO} from which we will take the cat and dog classes and the Oxford-IIT Pet Dataset \citep{catsdogs}, which comprises of images with labels for the 37 different cat and dog species that we will detect.
In these experiments, the backbone used will be EfficientNet-0, which will be used in the EfficientDet architecture as well as an independent EfficientNet backbone.
The base for the code of the detector uses this Pytorch implementation of EfficientDet \citep{pytorch-efficientdet}.
The base model is then modified to meet the needs of our experiments.

@@

\section{Detection, classification and segmentation}
Thinkkers do it like it is done in \citep{multinet} but use efficientnet for all parts?

\section{Recap}
This will be an overview of all the challenges and things about multi-task training based on the experiments we have done.

>>>>

\section{Multiple object classification tasks}
As we have previously covered, fine-tuning an ImageNet classifier often produces good results. 
Here we will take a pre-trained ImageNet backbone and learn multiple object classification tasks using the shared image embedding.
First, we will use two datasets that both contain images of healthy and unhealthy plants.

@@

\section{Object detection and image classification}
In this section, we will use multiple data sources and combine them into a single powerful object detector.
To be specific, our goal is to create an object detector for 37 different cat and dog species.
The two datasets that we will use are the COCO dataset \citep{COCO} from which we will take the cat and dog classes and the Oxford-IIT Pet Dataset \citep{catsdogs}, which comprises of images with labels for the 37 different cat and dog species that we will detect.
In these experiments, the backbone used will be EfficientNet-0, which will be used in the EfficientDet architecture as well as an independent EfficientNet backbone.
The base for the code of the detector uses this Pytorch implementation of EfficientDet \citep{pytorch-efficientdet}.
The base model is then modified to meet the needs of our experiments.

@@

\section{Detection and segmentation with EfficientDet}
In the EfficientDet paper \citep{efficientDet}, the authors point out that it is relatively simple to use the same EfficientNet backbone and BiFPN neck to do image segmentation as well.
Here we will attempt to train such a model but in a multi-task setting.
Our goal is to use the Kitti \citep{kitti} road segmentation data set to train a segmentation model, and the COCO dataset to train an object detector.
Since they both should be trainable on the same backbone and neck, we will see how good of a multi-task model we can create by sharing the entire detector.

Since we have not talked about image segmentation, we will briefly cover what it is about.
Image segmentation is also a very popular and important task with applications in many domains.
The goal for an image segmentation model is to determine the meaning of an image on a per-pixel level.
For example, in our case, we are going to train a model on the road segmentation data where the goal is to predict where the current lane goes, so we would like to know where the pixels that represent the current lane the car is on are.
So the output is a mask telling what class each pixel in the image belongs to.

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/segmentation-example.png}
\caption{An example of the annotations and an input image from the Kitti \citep{kitti} road segmentation data.}
\end{figure}

Here our goal is not to create a very accurate classifier but more to evaluate how difficult it is to take two very special problems and solve them by sharing as much as possible.
To create the model, we could use a U-Net \citep{unet}, which is an architecture specially designed for image segmentation.
We could adapt the U-Net architecture to EfficientNet and easily fit it with our backbone.
However, by using the EfficientDet, we get a chance to share more, and it is a much more advanced way of doing image segmentation, producing better results \citep{efficientDet}.

There is no complete implementation of the EfficientDet image segmentation head, and the authors don't really describe it too much in the paper.
To create the model, we took the EfficientDet detector as a base and augmented it with a segmentation head.
The segmentation head was based on the implementations of BiFPN segmentation from \citep{segment_pytorch}.
After creating multiple multi-task models, the creation and modification of the training loop were no longer so difficult to adjust to the new task.
Figuring out exactly how to add the new task into the existing model architecture took a while to find the exact values that the segmentation model needs for creating outputs.
After configuring data loaders and the model, the training was pretty much along the lines of the previous models we have covered.
The results for our models were along the lines that we have seen previously, the multi-task model being a few points below the single-task models.
It could be possible here that the segmentation model could get better if it had its own BiFPN network and could only share the backbone with the detector, but we did not have enough time to run all possible experiments.
Our modified EfficientDet architecture is shown in Figure 6.7.

\begin{figure}[h!] 
    \centering 
    \includegraphics[width=0.8\textwidth]{imgs/efficientdet-multi.png}
    \caption{EfficientDet model with segmentation and detection heads.}
\end{figure}

With the segmentation head and object detector head configured, it would now be easy to extend this model further.
We could easily add a new image classification head using the same backbone, like \citep{multinet}, where a single model is used for road segmentation, car detection, and road type classification.
Adding more classes to the segmentation or to the object classifier would be relatively easy to do.
Of course, there is a lot of sharing optimization to be done as well.
In our implementation, we naively shared everything, which was likely relatively detrimental to performance.
It would make sense to at least have the BiFPN be task-specific.
And since everything is now configured in the same model, it would be relatively easy to chop half of the backbone for each task and possibly get better results.
As we have covered over and over again, the space for possible improvements is huge.

\section{Overview of the experiments}
Based on our experiments, we can say that multi-task learning is hard when compared to training single-task models.
Training multiple single-task models is easier and faster and requires less user input and parameter optimization.
The effect of many parameters, like the learning rate, can be evaluated relatively easily based on a few epochs in a single task setting.
Perhaps to find the very best model, more experimentation and exploration is needed, but just some default values can generally provide good results.

For someone with little experience in training multi-task models, it can be difficult to get started.
Whereas it is easy to find multiple examples of just how a training loop should be created, finding such examples for multi-task models is much more difficult.
For experimenting with different ways of splitting the features into local and global features, it is important to have systems for easily doing experiments on different architectures.
In our experiments, we created four points where it was possible to cut the last block in the ResNet, for example, so it was easy to create models that each had none to some local features.
Devising ways to split on a more fine-grained level and grouping tasks when there are multiple would be extremely important when searching for the optimal architecture.
Manually changing how the weights are shared would not be enough.
In our experiments, this was also quite clear, as we did not experiment beyond having models that have some or none local features.
We did not do any experiments where we would have grouped the features in a more well thought out way.
Likely, most benefits are gained when multiple tasks share half of the networks instead of only having a head be local.
This would make sense as the lower level features are more general and likely there would not be as many conflicts as in the deeper layers.
The number of things to tune is also quite discouraging when the model does not train properly.
Finding out which part of the modifications to the default process is wrong can be extremely difficult.
Some of the mistakes we encountered were difficult and frustrating to solve. 
For example, we forgot to do a deep copy of the local features and just passed the same features as references to all tasks and wondered why the training of a single task was impacting others so much.
Or when we froze all local features except the head when we meant only to freeze all the global features.
Or mixing up the order of the tasks in the model task heads, so the final inferences ended up being complete garbage.

The impact of the various parameters that have to be picked seemed to be much larger.
With an incorrect sampling ratio, the models could be extremely far from the good sampling ratios.
It seems that finding the perfect sampling ratio might not be possible, and settling for a good enough one might be a good idea.
It seems that it may be a good idea to pick a lower learning rate than normal to find the best intersection of features.

Finally, the model structure's changes to create the various classifiers' heads can be difficult to add.
While adding multiple image classifiers is relatively trivial to do if one is comfortable doing basic model definitions, it can be difficult to combine the various task heads for the more complex tasks.
For example, object detector models are generally provided with very specific training loops, so getting an object detector that has a classifier head is much more difficult than just training the two separately.
Without some easy way of abstracting the classifier heads and automatically injecting them into the training loop, it may not be possible for some to create multi-task models without extensive help.
We considered relatively simple tasks that already had open-source implementations and mostly combined them into a single model.
When dealing with some more advanced models like some of the ones presented in the multi-tasking chapter, it would be even more difficult to create the models.

Despite all the challenges, we did manage to create models that came close or were equal to their single-task counterparts.
The multi-task models were smaller and faster in those cases, confirming that using the shared representations can be an excellent idea.

### 2020-05-31 __latexindent_temp.tex
Add final chapter recap and other minor fixes

\chapter{Conclusions}
In this thesis, we have given an overview of fundamental computer vision tasks of image classification and object detection.
We described the importance of the ImageNet data set and some of the most significant image classification architectures based on it.
The importance of these models extend beyond just solving the ImageNet dataset, and we covered how it is possible to apply the trained models in new classification problems with transfer learning.

For object detection, we described how the problem and datasets differ from image classification ones.
We also described the different parts of object detectors and how single and two-stage detectors differ from one another and when one might be preferred over the other.
The object detectors also show how important the ImageNet backbones are, as they are an integral part of the object detection architectures also.
The focal loss is an important loss function used by modern single-stage object detectors in allowing a large number of anchor points for localizing the objects in the images.
Finally, we described one of the current state-of-the-art object detection architectures, the EfficientDet, and how it can be trained on a new problem using transfer learning like in the case of image classification.

Here we have also presented multi-task learning as a generalization of transfer learning.
In a multi-task setting, the goal is to solve multiple tasks using some shared representation. 
It differs from transfer learning in that all tasks are optimized continuously, rather than just serving as a starting point.
Doing transfer learning is an excellent way of obtaining good results, even on little data.
With multi-task training, we can utilize the common model architectures as shared parameters for multiple tasks to allow the model to generalize better and run more efficiently.
This is possible because the model is required to use the same capacity to solve multiple problems that may require different features, some of which can also be useful in other tasks. 
Still, sometimes the multi-task setting can be detrimental to accuracy.
Despite the differences in performance, utilizing shared representations means that there are fewer parameters that the model needs to learn, leading to smaller models and shorter inference times.

We saw multiple examples where multi-task learning played an important part in getting models that are efficient and performant.
One of these was the object detection, where the model tries to classify and localize the objects.
Both soft and hard parameter sharing for multi-task learning were covered, with some specialized architectures taking advantage of the fact that multiple tasks are solved at the same time.
Finally, we found that multiple tasks can serve as auxiliary targets for training to aid the model in finding important features.

A multi-task problem setting modifies the training process and introduces some new parameters that can be tuned when training models.
Task-specific sampling ratio during the data sampling process and giving task-specific loss weights were the two new factors that need to be tuned when different tasks are combined.
These weights need to be tuned appropriately for the model to be able to find the features that work for all tasks.
Beyond just tuning parameters, multi-task models may need some architectural fine-tuning in deciding which tasks should have shared representations and just how much should be shared.

The training process differences due to the multi-task problem setting were evaluated through multiple experiments on combining various datasets into a single model.
With these experiments, we empirically verified some of the assumptions of training the models in a multi-task setting.
We noted that it was difficult to find the very best models as different sampling ratios resulted in very different final models.
As the model gets larger and the number of tasks increases, finding the correct ratios gets ever more difficult.
After adding new tasks, the previous ratios might also need adjusting.
Also, we discussed the difficulties of modifying the existing models to contain our desired output heads.
This was most apparent in the case of object detectors. 
The supplied code is relatively pre-packaged to run on the specified training loop, and modifying these model definitions to add new tasks takes some effort.
We saw some improvements and reductions in the model performance, but in general, the multi-task models were close to the single-task counterparts so that reducing the model size might be a good trade-off.

In all of our experiments, we could have spent more time on them to do more trials trying over different parameters and combinations of parameters.
Maybe by doing more thorough and systematic testing, it could be possible to evaluate exactly the effect of tuning a specific parameter.
Doing all the experiments would take a long time, and it is questionable whether the results would generalize to all problems.
The fact is that there are too many things that could be tuned, so it is difficult to determine which parameter should be tested.

Multi-task learning is a significant paradigm for creating large machine learning systems.
As it isn't really scalable, nor does it really make any sense to try to solve every task separately in a system that would be called intelligent.
For example, Andrej Karpathy, the Director of AI at Tesla, has given multiple talks on how they apply multi-task learning and how it is an instrumental part of their convolutional models \citep{karpathy}.
The problems he describes their teams tackle are the same problems that we have encountered and tried to solve in this thesis.
Like deciding what tasks should share and picking the correct sampling ratios are some of the problems Karpathy brings up as some of the most significant issues in training their models.
It does make sense that a camera-based self-driving car is one of the largest current multi-task learning applications as it is a problem that benefits from all the boons of multi-task learning we have covered.
It is important to have small models for running inference in constrained environments faster than single-task counterparts.
By sharing weights between tasks that have been specially picked in a way that they can augment each other makes it easier to learn new tasks and improve performance on the existing ones.
Having separate datasets for each task allows for the easy creation of new tasks in the model irrespective of others.
The ability to modify the loss weights and task sampling ratios allows for focusing on the critical tasks that are not allowed to fail.
So, while it likely is more difficult to train a model that solves all the tasks together, it is most likely unavoidable.
Single-task models that would solve the same tasks with the same real-time requirements would likely have to be so small that they would be unusable.
These are the kinds of problems where it is impossible to avoid using multi-task learning. 
With the correct techniques, it is possible to create systems that can reliably augment people's abilities.

In the end, what we learned is that the success of creating multi-task models out of some tasks can't be pre-determined currently. 
Some expensive experimentation is needed to arrive at the best multi-task architecture and to find the optimal parameters to train the model.  
Thus, multi-task learning can be considered as a trade-off of training time complexity for inference-time benefits in accuracy and speed.

>>>>

\chapter{Introduction}
Since 2012 computer vision research has been increasingly dominated by approaches using deep Convolutional Neural Networks (CNNs). These CNN based techniques have allowed for achieving significantly better results in computational image and video understanding compared to previous state-of-the-art approaches. Nowadays, there are many interesting avenues of computer vision research, such as image segmentation, object detection, object recognition, image captioning, pose detection, and many more. Since the task of computational image understanding is quite complex, the CNNs used to solve these problems often require dozens, if not hundreds of millions of parameters, in order to achieve sufficiently reliable accuracies. As the number of parameters is high, the networks require large computational resources to find optimal values for all of the variables in all of the hundreds of layers of matrices. Graphics Processing Units (GPUs) or Tensor Processing Units (TPUs) are the tools that people use to train the parameters in the networks since the training operations are highly parallelizable, allowing for the training of networks with hundreds or even thousands of layers. The problem often is that when training, one wants to increase the batch size, but at the same time, the computations must fit in the memory of the processing unit, which can be difficult to increase. Also, as the number of parameters in the model increases, the memory required for training the networks, and the time to produce outputs increases. To combat these problems, we often have to get better or more hardware, which can be expensive or compromise in the size of the model, which may lead to unreliable performance.

Embedded devices can use these CNN based algorithms to analyze their surroundings in an environment where they can't rely on external predictions from the cloud. One of the most significant issues is that achieving scene understanding requires multiple classifiers to solve various tasks. For example, a camera-based self-driving car has numerous things it is interested in resolving using the video output of its cameras. The tasks could be, for example, finding and classifying other vehicles, traffic signs, road markings, predicting paths of vehicles, pedestrians, and other actors, understanding where it can move, and finally deciding the steering angle and acceleration for the car with the information. All these tasks have to be solved using the limited computing capability onboard the actor, and the inference time for them can't be too long in order to react to everything within a reasonable time frame. Here we have many tasks, and if every task requires its independent network to produce the outputs, and we cut down on the network sizes, the classifiers might be powerful enough to produce safe outputs. On the other hand, if we don't reduce the network sizes, our inference time might be too long for a real-time system. One way to possibly get a good compromise between inference time and model complexity is to use multi-task learning and weight sharing within the model to get a single model with multiple outputs and similar or better performance to individual classifiers.

Multi-task learning proposes some solutions to these problems but makes the training process more difficult. Still, in some cases, it is something that has to be done to get a good enough inference time and accuracy on the problem at hand. Many modern computer vision models already feature an ImageNet backbone as a part of the classifier, so this is a good part of the network to consider for sharing. 
However, finding which tasks and how much can be shared is a difficult problem to solve.

\section{Scope of study}
In this thesis, we will present state-of-the-art solutions to fundamental computer vision problems, like image classification and object detection.
We will present the architectures of these models and show how the ImageNet backbones are an essential part of solving these problems.
Using the presented solutions, we will make use of various data sets to train multi-task models and evaluate the effects of training multi-task models.

\section{Structure of thesis}
Chapter 2 will present some basic terminology for describing convolutional neural networks that will be used throughout the thesis.
We won't cover the very basics of neural networks or the exact inner workings of convolutional neural networks, and refer to \citep{deep-learning} for studying those details.

Chapter 3 covers the modern image classification models, describing their architecture and how to train them.
We will also describe why the ImageNet is such a valuable data set to so many problems.
We will demonstrate the significance of the ImageNet models by defining transfer learning and describing how it is instrumental in solving small-scale problems with the ImageNet models as backbones.

Chapter 4 covers the basics of multi-task learning in terms of how it can be applied to computer vision problems.
Multi-task learning is also a useful technique in other domains of machine learning, but we focus only on computer vision. 
We will define multi-task learning and see how it relates to transfer learning.
Also, the basic differences of multi-task training to a single-task setting are described, and some examples of multi-task models are shown.
Finally, the theoretical benefits and issues that may arise are talked about and demonstrated using some examples.

Chapter 5 describes what object detection is and how to evaluate object detection models.
We will also briefly discuss the basic parts of an object detector and the difference between single and two-stage object detectors.
Finally, we will cover the EfficientDet architecture in detail and explain how to train an object detector by using it.

In chapter 6, we will cover the results of our experiments on training multi-task models.
The first experiment is about training image classifiers on plant imagery.
The second experiment is about training multi-label classifiers.
The third experiment covers training object detectors with multiple datasets.
The fourth experiment uses a single EfficientDet to do image segmentation and object detection.
Finally, we will summarize our experiences in training multi-task models and explain what problems we encountered.
